Systematic Design of Optimal Low-Thrust Transfers for the Three-Body Problem \thanks{This research has been supported in part by NSF under the grants CMMI-1243000 (transferred from 1029551), CMMI-1335008, and CNS-1337722.}

### 2017-07-11 manuscript.tex
Update trajectory plot in integrator comparison
Update discussion of comparision between conventional and variational integrator
Reviewer 1 Comment 19 and 21

                \caption{Trajectory comparison} \label{fig:compare_trajectory} 

@@

\Cref{fig:compare_trajectory} shows the trajectory of the spacecraft in the rotating reference frame for both integration schemes.

@@

The discrete equations of motion are an accurate approximation for the continuous dynamics as they closely match the solution of ODE45 over the initial portion of the simulation.
However, as time progresses the trajectories begin to diverge due to the differences in system energy.

@@

Over long simulation horizons or with the addition of small control inputs this poor energy behavior limits the applicability of conventional techniques in which energy conservation is mandatory for characterizing the solution space.

>>>>

                \caption{Earth-Moon three-body trajectory used for integrator comparision} \label{fig:compare_trajectory} 

@@

\Cref{fig:compare_trajectory} shows the trajectory of the spacecraft in the rotating reference for this comparison.

@@

@@

Over long simulation horizons or with the addition of small control inputs the inability of conventional integration schemes to accurately track the system energy limits the applicability of conventional techniques in which energy conservation is mandatory for characterizing the solution space.
